Optimizing Structural Properties Of Neural Networks With Evolutionary Algorithms

### 2015-07-31 paper/paper.tex
test

	\usepackage{amsmath}%,amssymb} 
	\usepackage{makeidx}
	\usepackage{amsfonts}
	\usepackage[ansinew]{inputenc}
	\usepackage[usenames,dvipsnames]{pstricks}
	\usepackage{subfigure}
	\usepackage{epsfig}
	\usepackage{pst-grad} % For gradients
	\usepackage{pst-plot} % For axes
	\usepackage[colorlinks,hyperindex]{hyperref}
	\hypersetup
	{
		colorlinks,%
		citecolor=black,%
		linkcolor=black,%
		urlcolor=black,%
	}

@@

>>>>

	\usepackage{amsmath}%,amssymb} 
	\usepackage{makeidx}
	\usepackage{amsfonts}
	\usepackage[ansinew]{inputenc}
	\usepackage[usenames,dvipsnames]{pstricks}
	\usepackage{subfigure}
	\usepackage{epsfig}
%	\usepackage{pst-grad} % For gradients
	\usepackage{pst-plot} % For axes
	\usepackage[colorlinks,hyperindex]{hyperref}
	\hypersetup
	{
		colorlinks,%
		citecolor=black,%
		linkcolor=black,%
		urlcolor=black,%
	}

@@

\paragraph{Tasks}
For the optimization to work properly, the problems presented to the networks 
have (for the most part) to solvable by FORCE learning. While it was shown \cite{}
that large recurrent neural networks are capable of learning very complex functions
using the FORCE algorithm, the optimization requires a large number of learnings.
Therefore, the networks have to be restricted to being quite small ($\approx 100$ neurons)
and as such are less powerful.

To get a simple criterion to estimate whether it might be possible to learn a given function 
using FORCE with 100 neurons, we look at
